KidsAIR: merge health datasets

### 2020-06-29 manuscript_tables_figures.Rmd
update data cleaning

---
title: 'KidsAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 13 May 2020, Updated 26 June 2020"
output:
  powerpoint_presentation: default
---

@@

```{r}
# number of households, total and by area
study_homes <- health_exposure_data_sampling_day %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>%
  count(area, winter_id, treatment_assigned)
study_homes

study_kids <- health_exposure_data_sampling_day %>% 
  filter(!is.na(child_id_num)) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>%
  count(area, winter_id, treatment_assigned)
study_kids

nn_homes <- health_exposure_data_sampling_day %>% 
  filter(home == "CH209" | home == "CH218")
```

>>>>

---
title: 'KidsAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 13 May 2020, Updated 29 June 2020"
output:
  powerpoint_presentation: default
---

@@

# Count number of kids initially randomized
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

ak_demographics <- read_rds(paste0(file_path, "Output/ak_demographic_data.rds"))
nn_demographics <- read_rds(paste0(file_path, "Output/nn_demographic_data.rds"))
wmt_demographics <- read_rds(paste0(file_path, "Output/wmt_demographic_data.rds"))

kids_demographics <- rbind(ak_demographics, nn_demographics, wmt_demographics) %>% 
  filter(!is.na(treatment)) %>% 
  filter(!is.na(child_id_num)) %>% 
  count(area, winter_id, treatment) %>% 
  filter(winter_id != 2)
```

# Count number of households initially randomized
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

ak_ids <- read_rds(paste0(file_path, "Output/ak_ids_linked.rds"))
nn_ids <- read_rds(paste0(file_path, "Output/nn_ids_linked.rds"))
wmt_ids <- read_rds(paste0(file_path, "Output/wmt_ids_linked.rds"))

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids) %>% 
  filter(!is.na(treatment)) %>% 
  ### WMA222 and WMA 233 had a treatment but no kids - not counting in flow chart
  filter(home != "WMA222" & home != "WMA233") %>%
  count(area, winter_id, treatment) %>% 
  filter(winter_id != 2)
```

# Count number of households and kids that participated by area and winter
```{r}
# number of households, total and by area
study_homes <- health_exposure_data_sampling_day %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>%
  count(area, winter_id, treatment_assigned)

study_kids <- health_exposure_data_sampling_day %>% 
  select(area, home, child_id_char, child_id_num, winter_id, treatment_assigned) %>% 
  filter(!is.na(child_id_char)) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  count(area, winter_id, treatment_assigned)
```

### 2020-06-29 merge_health_datasets.Rmd
update data cleaning

health_exposure_data_sampling_day <- health_data_merged %>% 
  select(-pm_mean_sampling_day, -pm_mean_sampling_period) %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  full_join(exposure_analysis_data_medium,
            by = c("area", "child_id_num", "home", "home_winter_id", "winter_id", 
                   "treatment_assigned", "treatment_actual",
                   "sampling_day")) %>% 
  filter(!is.na(home))

>>>>

demographics <- read_rds(paste0(file_path, "Output/demographics_final.rds")) %>% 
  select(child_id_num, child_id_char, area, winter_id)

health_exposure_data_sampling_day <- health_data_merged %>% 
  select(-pm_mean_sampling_day, -pm_mean_sampling_period) %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  full_join(exposure_analysis_data_medium,
            by = c("area", "child_id_num", "home", "home_winter_id", "winter_id", 
                   "treatment_assigned", "treatment_actual",
                   "sampling_day")) %>% 
  filter(!is.na(home)) %>% 
  filter(!is.na(child_id_num)) %>% 
  select(-child_id_char) %>% 
  left_join(demographics, by = c("area", "winter_id", "child_id_num")) %>% 
  select(area:child_id_num, child_id_char, visit_date:rh_max_5)
